### 2018-08-13 introduction.tex
huff edits

Modeling liquid-fueled systems with existing neutron transport and depletion 
tools is challenging because most of these tools are designed for the 
solid-fueled reactors simulation. The fuel material flows and potential online 
separations or feeds of specific elements or nuclides are the main challenges
of liquid-fueled systems. Furthermore, no established tool for liquid-fueled 
\gls{MSR} neutronics and fuel cycle evaluation exist, though internally 
developed tools from universities and research institutions can approximate 
online refueling \cite{serp_molten_2014}. The foundation for these tools was 
based on early \gls{MSR} simulation methods at \gls{ORNL}, which integrated 
neutronics and fuel cycle codes (i.e., ROD \cite{bauman_rod:_1971}) into 
operational plant tools (i.e., MRPP \cite{kee_mrpp:_1976}) for \gls{MSR} and 
reprocessing system design. More recent research efforts in Europe and Asia 
mainly focus on fast spectrum reactor fuel cycle analysis and couple external 
tools to neutron transport and depletion codes take into account continuous 
feeds and removals in \glspl{MSR}. Four of these efforts are listed in 
table~\ref{tab:fs_codes}.

>>>>

Liquid-fueled systems present a challenge to existing neutron transport and 
depletion tools which are typically designed to simulate solid-fueled reactors.  
To handle the material flows and potential online removal and feed of 
liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP} 
\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
this approach, recent tools from universities and research institutions can 
approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis 
and couple external tools to neutron transport and depletion codes take into 
account continuous feeds and removals in \glspl{MSR}. Four of these efforts are 
listed in table~\ref{tab:fs_codes}.
